Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-14 ipsj/paper.tex
Update References

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS \cite{par:TINET+TECS}, is comprised, and it is possible to utilize TINET function from mruby programs.

@@

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as a variable (Line 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Line 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Line 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.

>>>>

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{mrubyonTECS3}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.

@@

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as a variable (Line 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3} which is introduced in Section \ref{sec:mrubyonTECS}.
Line 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Line 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
